Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators

### 2019-09-11 PaperMagneticProfiles_JBSMSE.tex
Add first draft of conclusions.

>>>>

\section{Final considerations}
\label{sec:final-considerations}

To the authors' knowledge, this is the first study where magnetic profiles for AMR model are mathematically modeled and the model parameters are changed in a systematic way.

The instantaneous profile yields higher cooling capacity, even by
reducing the blow fraction on rectified cosine, up to levels achieved by pumping and valving systems, mainly restricted by valve opening times

The ramp profile is a feasible approximation for the instantaneous
profile, and can be optimized for increasing cooling capacity.
In particular, by synchronizing the plateau durations between fluid
and magnetic profiles.
